Optimal management of a stochastically varying population when policy adjustment is costly

### 2013-11-07 inst/doc/policycosts/policycosts.Rnw
update pdf

\documentclass{article}\usepackage{graphicx, color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.2, 0.2, 0.2}
\newcommand{\hlnumber}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlfunctioncall}[1]{\textcolor[rgb]{0.501960784313725,0,0.329411764705882}{\textbf{#1}}}%
\newcommand{\hlstring}[1]{\textcolor[rgb]{0.6,0.6,1}{#1}}%
\newcommand{\hlkeyword}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlargument}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlcomment}[1]{\textcolor[rgb]{0.180392156862745,0.6,0.341176470588235}{#1}}%
\newcommand{\hlroxygencomment}[1]{\textcolor[rgb]{0.43921568627451,0.47843137254902,0.701960784313725}{#1}}%
\newcommand{\hlformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hleqformalargs}[1]{\textcolor[rgb]{0.690196078431373,0.250980392156863,0.0196078431372549}{#1}}%
\newcommand{\hlassignement}[1]{\textcolor[rgb]{0,0,0}{\textbf{#1}}}%
\newcommand{\hlpackage}[1]{\textcolor[rgb]{0.588235294117647,0.709803921568627,0.145098039215686}{#1}}%
\newcommand{\hlslot}[1]{\textit{#1}}%
\newcommand{\hlsymbol}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlprompt}[1]{\textcolor[rgb]{0.2,0.2,0.2}{#1}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_1}

\end{knitrout}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_2}

\end{knitrout}

  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_3}

\end{knitrout}

  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
\end{figure}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_4a}

\end{knitrout}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_4b}

\end{knitrout}

\caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_5a}

\end{knitrout}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_5b}

\end{knitrout}

\caption*{Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Using\ \ as id variables}}\end{kframe}
\includegraphics[width=\maxwidth]{figure/Figure_6}

\end{knitrout}

@@

\begin{figure}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/Figure_7}

\end{knitrout}

\end{figure}

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlrrrrrr}
  \hline
 & penalty\_fn & ignore\_cost & ignore\_fraction & assume\_cost & assume\_fraction & sigma\_g & reduction \\ 
  \hline
1 & L1 & 14536.09 & 1.00 & 16857.61 & 1.00 & 0.05 & 0.10 \\ 
  2 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.10 \\ 
  3 & fixed & 13584.97 & 0.92 & 17582.78 & 1.05 & 0.05 & 0.10 \\ 
  4 & L1 & 9273.66 & 1.09 & 17561.81 & 1.04 & 0.05 & 0.20 \\ 
  5 & L2 & 11020.10 & 0.76 & 15538.44 & 0.92 & 0.05 & 0.20 \\ 
  6 & fixed & 8332.45 & 0.84 & 17401.82 & 1.03 & 0.05 & 0.20 \\ 
  7 & L1 & -641.78 & 0.21 & 15451.25 & 0.92 & 0.05 & 0.30 \\ 
  8 & L2 & -272586.11 & -24.90 & 11567.12 & 0.69 & 0.05 & 0.30 \\ 
  9 & fixed & -1213.01 & -0.46 & 15519.95 & 0.92 & 0.05 & 0.30 \\ 
  10 & L1 & 18281.97 & 1.01 & 20973.56 & 0.99 & 0.20 & 0.10 \\ 
  11 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.10 \\ 
  12 & fixed & 16691.94 & 1.03 & 20143.80 & 0.95 & 0.20 & 0.10 \\ 
  13 & L1 & 12788.95 & 0.96 & 20663.21 & 0.97 & 0.20 & 0.20 \\ 
  14 & L2 & 12462.51 & 0.72 & 19392.85 & 0.91 & 0.20 & 0.20 \\ 
  15 & fixed & 12399.01 & 0.88 & 21289.21 & 1.00 & 0.20 & 0.20 \\ 
  16 & L1 & 9099.48 & 0.73 & 19999.07 & 0.94 & 0.20 & 0.30 \\ 
  17 & L2 & -6337.76 & -0.39 & 17765.33 & 0.83 & 0.20 & 0.30 \\ 
  18 & fixed & 7399.01 & 0.62 & 21969.84 & 1.03 & 0.20 & 0.30 \\ 
  19 & L1 & 30227.43 & 1.07 & 31377.07 & 0.94 & 0.50 & 0.10 \\ 
  20 & L2 & 33472.18 & 1.00 & 33472.18 & 1.00 & 0.50 & 0.10 \\ 
  21 & fixed & 28926.73 & 1.09 & 30500.85 & 0.91 & 0.50 & 0.10 \\ 
  22 & L1 & 24157.93 & 1.10 & 31767.92 & 0.95 & 0.50 & 0.20 \\ 
  23 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.20 \\ 
  24 & fixed & 23573.19 & 1.02 & 30069.80 & 0.90 & 0.50 & 0.20 \\ 
  25 & L1 & 21086.12 & 1.12 & 32035.93 & 0.96 & 0.50 & 0.30 \\ 
  26 & L2 & 19091.31 & 0.93 & 29225.46 & 0.87 & 0.50 & 0.30 \\ 
  27 & fixed & 17209.56 & 0.85 & 32946.24 & 0.98 & 0.50 & 0.30 \\ 
   \hline
\end{tabular}

\caption{Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value). These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$). Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $). }
\end{table}

>>>>

\documentclass{article}

\begin{document}
%\SweaveOpts{concordance=TRUE, echo=FALSE}

@@

<<settings, echo=FALSE, warning=FALSE>>=
require(knitr)
opts_chunk$set(echo=FALSE, dev="pdf", cache=FALSE, warning=FALSE)
require(pdgControl)
require(reshape2)
require(ggplot2)
require(data.table)
require(plyr)
require(xtable)
load("writeup.rda")
theme_set(theme_bw())
@

\begin{figure}
<<Figure_1>>=
ggplot(fees, aes(c2, (npv0-value)/npv0, col=variable)) + geom_point() + geom_line()
@

@@

\begin{figure}
<<Figure_2, fig.width=12>>=
p2 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, harvest_alt), col="grey20", lwd=1)  +
  geom_line(aes(time, harvest), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="havest intensity (fish taken)", title = "Harvest Policy Dynamics")
p2
@
  \caption{Individual realizations of optimal harvesting strategy under the different functional forms of adjustment costs.}
\end{figure}

\begin{figure}
<<Figure_3, fig.width=12>>=
p1 <- ggplot(subset(dt, replicate %in% names(reps)[1:5])) +
  geom_line(aes(time, alternate), col="grey20", lwd=1) +
  geom_line(aes(time, fishstock), col=rgb(0,0,1,.8)) + 
  facet_grid(replicate~penalty_fn) + 
  labs(x="time", y="stock size", title = "Stock Dynamics")
p1
@
  \caption{Individual realizations of optimal stock size strategy under the different functional forms of adjustment costs.}
\end{figure}

@@

\begin{figure}
<<Figure_4a>>=
Fig4a <- ggplot(harvest_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + 
  xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4))

Fig4b <- ggplot(harvest_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4)) 
Fig4a

@

@@

\begin{figure}
<<Figure_4b>>=
Fig4b
@
\caption*{Figure 4b: Autocorrelation of optimal harvest rates through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

\begin{figure}
<<Figure_5a>>=
fishstock_stats <- lapply(sims_at_each_apple, stats_fishstock)
fishstock_trends <- get_trends(fishstock_stats)

Fig5a <- ggplot(fishstock_trends, 
                aes(fraction, Ev, ymin=Ev-SDv, ymax=Ev+SDv, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs")+
  scale_x_continuous(limits=c(0, 0.4))

Fig5b <- ggplot(fishstock_trends, 
                aes(fraction, Ea, ymin=Ea-SDa, ymax=Ea+SDa, col=penalty)) + 
  geom_ribbon(aes(fill=penalty, col=NA), lwd=0, alpha=.05) + 
  geom_line() + xlab("Fraction of NPV lost to costs") +
  scale_x_continuous(limits=c(0, 0.4)) 
Fig5a

@

@@

\begin{figure}
<<Figure_5b>>=
Fig5b
@
\caption*{Figure 5b: Autocorrelation of optimal stock sizes through time as a function of size of adjustment penalties, the latter being calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs. }
\end{figure}

@@

\begin{figure}
<<Figure_6>>=
totals <- data.frame(
profit_under_penalty = dt[,sum(profit_fishing), by='replicate']$V1,
cost_under_penalty = dt[,sum(policy_cost), by='replicate']$V1,
profit_without_penalty = dt[,sum(profit_fishing_alt), by='replicate']$V1,
costs_ignoring_penalty = dt[,sum(policy_cost_alt), by='replicate']$V1)
totals <- melt(totals)
ggplot(totals) + geom_density(aes(value, fill=variable), alpha=.7)
@

@@

\begin{figure}
<<Figure_7>>=
require(ggplot2)
df <- read.csv("output.csv")
df <- df[2:8]
require(reshape2)
who <- c("penalty_fn", "ignore_fraction", "assume_fraction", "sigma_g", "reduction")
df2 <- melt(df, id=who)
who <- c("penalty_fn", "sigma_g", "reduction", "variable", "value")
df3 <- melt(df2, id=who)
names(df3) <- c("penalty_fn", "sigma_g", "reduction", "variable", "value", "fraction_variable", "fraction")

df3$reduction <- as.factor(df3$reduction)
ggplot(df3) + geom_line(aes(sigma_g, value, col=reduction, lty=variable)) + facet_wrap(~penalty_fn, scales="free_y") 
@
\end{figure}

@@

<<Table_1, results="asis">>=
df4 <- df[c(1,2,4,6,7)]
df4 <- plyr::arrange(df4, penalty_fn)
print(xtable::xtable(df))
@

Overall cost of assuming policy adjustment costs apply when they are absent (first value) or from ignoring them when they are present (second value). These overall costs are shown for different severities of policy adjustment costs (columns) and levels of environmental variability (rows) and for three different functional forms for policy adjustment costs ($\Pi_i$ for $ i=1-3$). Values expressed as percentages of the maximum expected net present value when no policy adjustment costs apply and this is known to managers ($ NPV_0 ({\bf h_0^*}) $).
